A Cloud Native Approach to Adversarial Robustness of Neural Networks

### 2024-03-30 plots/cifar/aft_comparison.tex
update plots

\begin{table*}
\centering
\caption{Comparison of AFR Models on the CIFAR dataset.}
\label{tab:cifar}
\begin{tabular}{lllrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & E50 \\
\midrule
Weibull & -1234.74 & -1234.74 & 0.79 & 0.80 & 0.02 & 0.00 \\
Cox & -- & -- & 0.80 & 0.80 & 0.01 & 0.00 \\
Log Logistic & -1335.65 & -1335.65 & 0.79 & 0.79 & 0.01 & 0.00 \\
Log Normal & -1387.92 & -1387.92 & 0.79 & 0.79 & 0.01 & 0.00 \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{table*}
\centering
\caption{Comparison of AFR Models on the CIFAR dataset.}
\label{tab:cifar}
\begin{tabular}{lllrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & E50 \\
\midrule
Weibull & -1.23e+03 & -1.23e+03 & 0.79 & 0.8 & 0.02 & 0 \\
Cox & -- & -- & 0.8 & 0.8 & 0.01 & 0 \\
Log Logistic & -1.34e+03 & -1.34e+03 & 0.79 & 0.79 & 0.01 & 0 \\
Log Normal & -1.39e+03 & -1.39e+03 & 0.79 & 0.79 & 0.01 & 0 \\
\bottomrule
\end{tabular}
\end{table*}

### 2024-03-30 plots/cifar100/aft_comparison.tex
update plots

\begin{table*}
\centering
\caption{Comparison of AFR Models on the CIFAR100 dataset.}
\label{tab:cifar100}
\begin{tabular}{lllrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & E50 \\
\midrule
Weibull & -1113.16 & -1113.16 & 0.78 & 0.76 & 0.00 & 0.00 \\
Cox & -- & -- & 0.79 & 0.76 & 0.02 & 0.00 \\
Log Logistic & -1198.31 & -1198.31 & 0.78 & 0.77 & 0.01 & 0.00 \\
Log Normal & -1244.92 & -1244.92 & 0.79 & 0.77 & 0.00 & 0.00 \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{table*}
\centering
\caption{Comparison of AFR Models on the CIFAR100 dataset.}
\label{tab:cifar100}
\begin{tabular}{lllrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & E50 \\
\midrule
Weibull & -1.11e+03 & -1.11e+03 & 0.78 & 0.76 & 0 & 0 \\
Cox & -- & -- & 0.79 & 0.76 & 0.02 & 0 \\
Log Logistic & -1.2e+03 & -1.2e+03 & 0.78 & 0.77 & 0.01 & 0 \\
Log Normal & -1.24e+03 & -1.24e+03 & 0.79 & 0.77 & 0 & 0 \\
\bottomrule
\end{tabular}
\end{table*}

### 2024-03-30 plots/mnist/aft_comparison.tex
update plots

\begin{table*}
\centering
\caption{Comparison of AFR Models on the MNIST dataset.}
\label{tab:mnist}
\begin{tabular}{lllrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & E50 \\
\midrule
Weibull & -1559.16 & -1559.16 & 0.90 & 0.90 & 0.02 & 0.00 \\
Cox & -- & -- & 0.90 & 0.89 & 0.03 & 0.00 \\
Log Logistic & -1672.54 & -1672.54 & 0.90 & 0.90 & 0.02 & 0.00 \\
Log Normal & -1711.45 & -1711.45 & 0.90 & 0.90 & 0.01 & 0.00 \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{table*}
\centering
\caption{Comparison of AFR Models on the MNIST dataset.}
\label{tab:mnist}
\begin{tabular}{lllrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & E50 \\
\midrule
Weibull & -1.56e+03 & -1.56e+03 & 0.9 & 0.9 & 0.02 & 0 \\
Cox & -- & -- & 0.9 & 0.89 & 0.03 & 0 \\
Log Logistic & -1.67e+03 & -1.67e+03 & 0.9 & 0.9 & 0.02 & 0 \\
Log Normal & -1.71e+03 & -1.71e+03 & 0.9 & 0.9 & 0.01 & 0 \\
\bottomrule
\end{tabular}
\end{table*}
